Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-25 analysis/paper/paper.Rmd
Correct tense in writing

The effect of *Phytopathologia Mediterranea* (Median = 1.68, 95% CI [0.78, 2.57]) had a 99.99% probability of being positive (\> 0), 99.98% of being significant (\> 0.05), and 99.83% of being large (\> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19017).

@@

However, the year of publication did not have an effect on the availability of data was accepted (Figure \@ref(fig:year-parameters)B, Table S4).
The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 21692).

>>>>

The effect of *Phytopathologia Mediterranea* (Median = 1.68, 95% CI [0.78, 2.57]) had a 99.99% probability of being positive (\> 0), 99.98% of being significant (\> 0.05), and 99.83% of being large (\> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 19017).

@@

However, the year of publication did not have an effect on the availability of data was accepted (Figure \@ref(fig:year-parameters)B, Table S4).
The effect of year (Median = 0.08, 95% CI [-8.06e-03, 0.18]) had a 96.19% probability of being positive (> 0), 75.92% of being significant (> 0.05), and 0.00% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices were reliable (ESS = 21692).
